The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
add caribou keyword
tidy intro p2

## Keywords
Rangifer, Social network analysis, Habitat selection, Landscape ecology, Space use

@@

Social interactions exists across both temporal and spatial scales [Figure \@ref(fig:spacetime), @Whitehead_2008].
For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas social associations
represent shared space use by members of the same social group over longer time periods [@Franks_2009], and home range overlap occurs over
coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
Although the social environment scales spatially and temporally, it
remains unclear whether coarser scales of social interactions, such as social
association and home range overlap, vary predictably [@Castles_2014;
@Farine_2015a; @Evans_2019]. Social scale 
is defined by the temporal and spatial scales across which different forms of sociality are measured  [@Farine_2015a].

>>>>

## Keywords
Caribou, *Rangifer*, Social network analysis, Habitat selection, Landscape ecology, Space use

@@

Social interactions exists across both temporal and spatial scales [Figure
\@ref(fig:spacetime), @Whitehead_2008]. For example, conspecific grooming
requires close spatial proximity and occurs over brief time periods 
[e.g. @Carter_2015], social associations represent shared space use by members of the
same social group over relatively longer time periods [@Franks_2009], and home
range overlap occurs over coarser spatial and temporal scales [e.g.
@Piza_Roca_2018]. Although the social environment scales spatially and
temporally, it remains unclear whether coarser scales of social behaviour, such
as social association and home range overlap, vary predictably 
[@Castles_2014; @Farine_2015a; @Evans_2019]. Thus, social scale is defined by 
the temporal and spatial scales across which different forms of sociality are measured
[@Farine_2015a].
